
  %-------------------------
  % Resume in LaTeX
  % Author : Your Name
  % License : MIT
  %-------------------------
  
  \documentclass[a4paper,11pt]{article}
  \usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry} % Page margins
  \usepackage{enumitem} % For item lists
  \usepackage{hyperref} % For hyperlinks
  \usepackage{titlesec} % For section titles
  \usepackage{xcolor} % For text color
  
  % Section formatting
  \titleformat{\section}{\large\bfseries\color{blue}}{}{0em}{}[\titlerule]
  \renewcommand{\labelitemi}{$\bullet$}
  
  \begin{document}
  
  \begin{center}
      {\LARGE Your Name} \\[0.5em]
      Your Address, City, State, ZIP \\[0.5em]
      \texttt{your.email@example.com} | (123) 456-7890 \\[0.5em]
      \href{https://github.com/yourusername}{GitHub} | \href{https://linkedin.com/in/yourusername}{LinkedIn}
  \end{center}
  
  \section*{Personal Information}
  \begin{itemize}[leftmargin=0.5cm]
      \item \textbf{Date of Birth:} January 1, 1990
      \item \textbf{Nationality:} Your Nationality
  \end{itemize}
  
  \section*{Education}
  \begin{itemize}[leftmargin=0.5cm]
      \item \textbf{Bachelor of Science in Computer Science} \\
      University Name, City, State \hfill Graduated: May 2022
      \begin{itemize}
          \item CGPA: 3.5/4.0
      \end{itemize}
  \end{itemize}
  
  \section*{Projects}
  \begin{itemize}[leftmargin=0.5cm]
      \item \textbf{Project Name} \hfill \textit{Month Year}
      \begin{itemize}
          \item Description of the project and your contributions.
          \item Technologies used: HTML, CSS, JavaScript, etc.
      \end{itemize}
  
      \item \textbf{Another Project Name} \hfill \textit{Month Year}
      \begin{itemize}
          \item Description of the project and your contributions.
          \item Technologies used: Python, Flask, etc.
      \end{itemize}
  \end{itemize}
  
  \section*{Experience}
  \begin{itemize}[leftmargin=0.5cm]
      \item \textbf{Intern, Software Development} \\
      Company Name, City, State \hfill June 2021 -- August 2021
      \begin{itemize}
          \item Developed features for a web application using React.
          \item Collaborated with the design team to improve user experience.
      \end{itemize}
  
      \item \textbf{Part-time, IT Support} \\
      Another Company Name, City, State \hfill January 2020 -- May 2021
      \begin{itemize}
          \item Provided technical support to clients.
          \item Assisted in setting up hardware and software.
      \end{itemize}
  \end{itemize}
  
  \section*{Skills}
  \begin{itemize}[leftmargin=0.5cm]
      \item \textbf{Programming Languages:} Java, Python, JavaScript
      \item \textbf{Web Technologies:} HTML, CSS, React, Node.js
      \item \textbf{Tools:} Git, Docker, VS Code
  \end{itemize}
  
  \end{document}
  